---
title: Nuevas Pizzas
subtitle: A minimalistic Quarto + Typst template for academic writing
author:
  - name: Pita
    email: menguadalupe@yahoo.com.mx
    orcid: 0009-0007-1967-8304
    affiliations:
      - name: Inecol
abstract: |
  Quiero decir cosas importantes.
thanks: |
  You can write acknowledgements here.
keywords:
  - Quarto
  - Typst
  - format
date: today
date-format: full
bibliography: references.bib
format:
  html: default
  docx: default
  academic-typst:
    section-numbering: "1.1.1"
execute:
  echo: false
---

This document shows a minimal example of the template. For more information, see the [full demo](https://kazuyanagimoto.com/quarto-academic-typst/template-full.pdf) and its [source](https://kazuyanagimoto.com/quarto-academic-typst/template-full.qmd).

# Datos

Section numbering can be specified in the YAML `section-numbering` field as other Typst templates.


```{r}
#| label: datos-redlist
#| warning: false

library(stringr)
library(flextable)

pacman::p_load(Microsoft365R)

# Autoriza el acceso a mi cuenta de OneDrive
od <- get_business_onedrive()
archivo <- "redlist.csv"

# Accedo al archivo de interés
redlist <- od$load_dataframe(archivo, show_col_type = FALSE)

names(redlist) <- c("estatus", "num")
Encoding(redlist$estatus) <-  "latin1"

flextable::flextable(redlist)

```


## Subsection as Heading Level 2

You can use LaTeX math expressions:

$$
Y_{it} = \mu_i + Status_i + \varepsilon_{it}.
$$

## Citation

You can cite a reference like this [@katsushika1831] or @horst2020. Typst has some built-in citation styles. Check the [Typst documentation](https://typst.app/docs/reference/model/bibliography/#parameters-style) for more information.
The Red List of Mexican Cloud Forest Trees

# Figures and Tables

## Figures

Como se muestra en la Figura 1 @fig-hist-redlist shows, the caption is displayed below the figure. As a caption of the figure (`fig-cap`), I use bold text for the title and use a normal text for the description.

```{r}
#| label: fig-hist-redlist
#| fig-cap: "**Figura 1. Número de especies propias de bosques de montaña por estatus de conservación.**"

# Create the histogram with facets
library(ggplot2)

redlist$est_ord <- factor(redlist$estatus, ordered = TRUE)

ggplot(redlist, aes(x = est_ord, y = num, fill = estatus)) +
  geom_bar(stat = "identity") +
  labs(title = "Número de especies propias de los bosques de montaña incluidas en la Redlist",
       x = "Estatus de Conservación",
       y = "num")

```

## Tables

You can use [tinytable](https://vincentarelbundock.github.io/tinytable/) for general tables and [modelsummary](https://vincentarelbundock.github.io/modelsummary/) for regression tables.[^1] As @tbl-mtcars-head shows, the caption is displayed above the table. The notes of the table can be added using the `notes` argument of the `tinytable::tt()` function.

[^1]: Since the default backend of `modelsummary` is `tinytable`, you can use the customization options of `tinytable` for `modelsummary`.

```{r}
#| label: tbl-mtcars-head
#| tbl-cap: Head of the mtcars Dataset

nt <- "_Notes_: This table shows the first six rows of the mtcars dataset."
mtcars[1:5, 1:5] |>
  tinytable::tt(width = 0.8, notes = nt)         
```

# Last words

I made this template for my working papers, so it may not be suitable for other fields than economics. I am happy to receive feedback and suggestions for improvement.

{{< appendix >}}

# Supplemental Figures

The figure numbering will be reset to "A.1", "A.2", etc so that it is clear that these figures are part of the appendix.


{{< pagebreak >}}
